---
title: "Monte Carlo Analysis for Verifying Expressions"
author: "Juri Trifonov"
output: html_document
---

## Core functions and packages
```{r}
library(sreg)
library(dplyr)
library(tidyr)
library(extraDistr)
library(tidyverse)
rm(list = ls())
source("/Users/trifonovjuri/Desktop/sreg/R/2.0(dev)/fun_new.r")
```

## Individual level treatment assignment
Here we provide the results for the case with multiple treatments but without clusters (one covariate so far).

```{r}
nsim <- 2000
tau_vec <- c(0.5, 1.5)
n.treat <- 2
k <- 3
n <- 1200
treat_sizes <- c(1, 1, 1)
theta_hat_mtrx <- matrix(ncol = n.treat, nrow = nsim)
v_hat_mtrx <- matrix(ncol = n.treat, nrow = nsim)
hit <- matrix(ncol = n.treat, nrow = nsim)

for (s in 1:nsim)
{
  data_raw <- dgp_po(n = n, theta.vec = tau_vec, n.treat = n.treat, gamma.vec = c(0.4, 0.2, 1)) # Checked that now it returns several X's
  data_df <- run_experiment_multi(data_raw, n.treat = n.treat, k = k, treat_sizes = treat_sizes) # 1 gets treatment 0, 1 gets treatment 1, 1 gets treatment 2 in each triplet
  data_full <- data.frame("Y" = data_df$y, "D" = data_df$A, "X" = data_df$X, "S" = data_df$block)
  #data_full <- data.frame("Y" = data_df$y, "D" = data_df$A, "X" = data.frame(data_df$X, "S" = data_df$block)
  N <- nrow(data_full)
  theta_hat_vec <- theta_hat_mult(data_full$Y, data_full$D, data_full$X, data_full$S)$tau.hat
  v_hat_vec <- var_hat_mult(data_full) / N
  theta_hat_mtrx[s, ] <- theta_hat_vec
  v_hat_mtrx[s, ] <- v_hat_vec
  upper <- theta_hat_vec + qnorm(0.975) * sqrt(v_hat_vec)
  lower <- theta_hat_vec - qnorm(0.975) * sqrt(v_hat_vec)
  hit[s, ] <- (tau_vec < upper) & (tau_vec > lower)
  print(s)
}
result_table <- data.frame(
  `True tau` = tau_vec,
  `E[tau_n]` = round(colMeans(theta_hat_mtrx), 4),
  `True Variance` = round(colMeans(v_hat_mtrx), 4),
  `E[V_n]` = round(apply(theta_hat_mtrx, 2, var), 4),
  `Coverage` = round(colMeans(hit), 4),
  check.names = FALSE
)
print(result_table)
```


## Cluster level treatment assignment
Here we provide the results for the case of cluster level treatment assignment with multiple treatments (one covariate so far).
```{r}
n_treat <- 3
nsim <- 10000
tau_vec <- c(0.2, 1.2, 0.7)
gamma_vec <- c(0.4, 0.2, 1)
tau_hat_mtrx <- matrix(ncol = n_treat, nrow = nsim)
var_hat_mtrx <- matrix(ncol = n_treat, nrow = nsim)
hit_mtrx <- matrix(ncol = n_treat, nrow = nsim)
G <- 500
Nmax <- 50
k <- 5
treat_sizes <- c(2, 1, 1, 1) # treatment 0 - p_1 individuals, treatment 1 - p_2 individuals, ...
max.support <- Nmax / 10 - 1
# Ng <- rep(Nmax, G)
Ng <- gen.cluster.sizes(G, max.support)

for (s in 1:nsim)
{
  data_pot <- dgp.po.creg(Ng = Ng, tau.vec = tau_vec, G = G, gamma.vec = gamma_vec, n.treat = n_treat)
  proba <- dgp.obs.creg(baseline = data_pot, n.treat = n_treat, k = k, treat_sizes = treat_sizes)
  data_cl <- data.frame("Y" = proba$Y, "D" = proba$D, proba$X, "S" = proba$S, "Ng" = proba$Ng, "G.id" = proba$G.id)
  tau_hat <- theta_hat_mult_cl_old(Y = data_cl$Y, D = data_cl$D, X = data_cl$x_1, S = data_cl$S, G.id = data_cl$G.id, Ng = data_cl$Ng)
  tau_hat_mtrx[s, ] <- tau_hat$tau.hat
  var_hat <- var_hat_mult_cl(Y = data_cl$Y, D = data_cl$D, X = data_cl$x_1, S = data_cl$S, G.id = data_cl$G.id, Ng = data_cl$Ng, tau.hat = tau_hat) / G
  var_hat_mtrx[s, ] <- var_hat
  upper <- tau_hat$tau.hat + qnorm(0.975) * sqrt(var_hat)
  lower <- tau_hat$tau.hat - qnorm(0.975) * sqrt(var_hat)
  hit_mtrx[s, ] <- (tau_vec < upper) & (tau_vec > lower)
  print(s)
}
result_table <- data.frame(
  `True tau` = tau_vec,
  `E[tau_n]` = round(colMeans(tau_hat_mtrx), 4),
  `E[V_n]` = round(colMeans(var_hat_mtrx), 4),
  `True Variance` = round(apply(tau_hat_mtrx, 2, var), 4),
  `Coverage` = round(colMeans(hit_mtrx), 4),
  check.names = FALSE
)
print(result_table)
``` 

```{r}
tau_vec <- c(0.5, 1.5) 
n.treat <- 2
k <- 3
n <- 900
treat_sizes <- c(1, 1, 1)


datim <- sreg.rgen(n = 1200, cluster = TRUE, small.strata = TRUE, tau.vec = c(1.2, 0.8))
X <- data.frame(datim$x_1, datim$x_2, datim$Ng)
sreg(Y = datim$Y, S = datim$S, D = datim$D, G.id = datim$G.id, Ng = datim$Ng, X = X, HC1 = TRUE, small.strata = TRUE)

data_raw <- dgp_po(n = n, theta.vec = tau_vec, n.treat = n.treat, gamma.vec = c(0.4, 0.2, 1)) # Checked that now it returns several X's
data_df <- run_experiment_multi(data_raw, n.treat = n.treat, k = k, treat_sizes = treat_sizes) # 1 gets treatment 0, 1 gets treatment 1, 1 gets treatment 2 in each triplet
Y <- data_df$y
D <- data_df$A
X <- data.frame("x_1" = data_df$x_1, "x_2" = data_df$x_2)#, 'bor' = rnorm(24, 2, 1), 'god' = rnorm(24, 3, 1), 'bro'= rnorm(24, 3, 1), 'bro1'= rnorm(24, 3, 1), 'bro2'= rnorm(24, 3, 1))
S <- data_df$block
data_full <- data.frame(Y, D, X, S)
N <- nrow(data_full)

theta_hat_vec <- theta_hat_mult(Y, D, X, S)#$tau.hat
var_hat_vec   <- var_hat_mult(Y, D, X, S, theta_hat_vec) / N

# Using the aggregated master functions to test:
tau_hat <- tau.hat.sreg.ss(Y, D, X, S)
var_hat <- as.var.sreg.ss(Y, D, X, S, fit = tau_hat) / N
var_hat <- as.var.sreg.ss(Y, D, X, S, fit = tau_hat, HC1 = TRUE) / N
sqrt(var_hat)
tau_hat <- tau.hat.sreg.ss(Y, D, X = NULL, S)
var_hat <- as.var.sreg.ss(Y, D, X = NULL, S, fit = NULL, HC1 = TRUE) / N
X <- data.frame("age" = data_df$x_1)#, "x_2" = data_df$x_2)#, 'bor' = rnorm(24, 2, 1), 'god' = rnorm(24, 3, 1), 'bro'= rnorm(24, 3, 1), 'bro1'= rnorm(24, 3, 1), 'bro2'= rnorm(24, 3, 1), 'bro3' = rnorm(24, 5, 2))
agg_result <- res.sreg.ss(Y, S, D, X, HC1 = TRUE)
agg_result$data
any(sapply(agg_result$beta.hat, function(x) any(is.na(x))))
any(sapply(agg_result$se.rob, function(x) any(is.infinite(x))))
abju <- sreg(Y, S = S, D, G.id = NULL, Ng = NULL, X = NULL, HC1 = TRUE, small.strata = TRUE)
abju$lin.adj

nsim <- 1000
n <- 1200
k <- 3
theta_vec <- c(0.5, 1.5)
n.treat <- 2
treat_sizes <- c(1, 1, 1)
theta_hat_mtrx <- matrix(nrow = nsim, ncol = n.treat)
var_hat_mtrx <- matrix(nrow = nsim, ncol = n.treat)
hit_mtrx <- matrix(nrow = nsim, ncol = n.treat)
for (s in 1:nsim)
{
  data_raw <- dgp_po(n = n, theta.vec = theta_vec, n.treat = n.treat, gamma.vec = c(0.4, 0.2, 1)) # Checked that now it returns several X's
  data_df <- run_experiment_multi(data_raw, n.treat = n.treat, k = k, treat_sizes = treat_sizes) # 1 gets treatment 0, 1 gets treatment 1, 1 gets treatment 2 in each triplet
  Y <- data_df$y
  D <- data_df$A
  X <- data.frame("x_1" = data_df$x_1, "x_2" = data_df$x_2)
  S <- data_df$block
  data_full <- data.frame(Y, D, X, S)
  N <- nrow(data_full)

  fit <- theta_hat_mult(Y, D, X, S)
  theta_hat_vec <- fit$tau.hat
  var_hat_vec <- var_hat_mult(Y, D, X, S, fit) / N

  theta_hat_mtrx[s, ] <- theta_hat_vec
  var_hat_mtrx[s, ] <- var_hat_vec

  upper <- theta_hat_vec + qnorm(0.975) * sqrt(var_hat_vec)
  lower <- theta_hat_vec - qnorm(0.975) * sqrt(var_hat_vec)
  hit_mtrx[s, ] <- (theta_vec < upper) & (theta_vec > lower)
  print(s)
}

colMeans(theta_hat_mtrx)
colMeans(var_hat_mtrx)
apply(theta_hat_mtrx, 2, var)

colMeans(hit_mtrx)
data_full %>%
  group_by(S) %>%
  summarize(
    Y_treated = mean(Y[D == 1], na.rm = TRUE),
    Y_control = mean(Y[D == 0], na.rm = TRUE),
    X_treated = list(colMeans(X[D == 1, , drop = FALSE], na.rm = TRUE)),
    X_control = list(colMeans(X[D == 0, , drop = FALSE], na.rm = TRUE)),
    k = n(),
    l = sum(D == 1),
    q = sum(D == 0),
    .groups = "drop"
  )


agg_data_old <- data_full %>%
  group_by(S) %>%
  summarize(
    Y_treated = mean(Y[D == 1], na.rm = TRUE),
    Y_control = mean(Y[D == 0], na.rm = TRUE),
    X_treated = list(colMeans(X[D == 1, , drop = FALSE], na.rm = TRUE)),
    X_control = list(colMeans(X[D == 0, , drop = FALSE], na.rm = TRUE)),
    k = n(),
    l = sum(D == 1),
    q = sum(D == 0),
    .groups = "drop"
  )

# Turn list columns into two separate columns per covariate
agg_data_old <- agg_data_old %>%
  mutate(
    X_treated_1 = map_dbl(X_treated, 1),
    X_treated_2 = map_dbl(X_treated, 2),
    X_control_1 = map_dbl(X_control, 1),
    X_control_2 = map_dbl(X_control, 2)
  )

# Now view the first few rows
agg_data_old


agg_data <- data_full %>%
  group_split(S) %>%
  map_dfr(~ {
    df <- .
    list(
      S = df$S[1],
      Y_treated = mean(df$Y[df$D == 1], na.rm = TRUE),
      Y_control = mean(df$Y[df$D == 0], na.rm = TRUE),
      X_treated = list(colMeans(df[df$D == 1, grep("^x_", names(df)), drop = FALSE])),
      X_control = list(colMeans(df[df$D == 0, grep("^x_", names(df)), drop = FALSE])),
      k = nrow(df),
      l = sum(df$D == 1),
      q = sum(df$D == 0)
    )
  })

# Turn list columns into two separate columns per covariate
agg_data <- agg_data %>%
  mutate(
    X_treated_1 = map_dbl(X_treated, 1),
    X_treated_2 = map_dbl(X_treated, 2),
    X_control_1 = map_dbl(X_control, 1),
    X_control_2 = map_dbl(X_control, 2)
  )
```

```{r}
n_treat <- 3 
nsim <- 10
tau_vec <- c(0.2, 1.2, 0.7)
gamma_vec <- c(0.4, 0.2, 1)
# n.treat = 2
k <- 5
treat_sizes <- c(2, 1, 1, 1)
tau_hat_mtrx <- matrix(ncol = n_treat, nrow = nsim)
tau_hat_mtrx_old <- matrix(ncol = n_treat, nrow = nsim)
var_hat_mtrx <- matrix(ncol = n_treat, nrow = nsim)
var_hat_old_mtrx <- matrix(ncol = n_treat, nrow = nsim)
hit_mtrx <- matrix(ncol = n_treat, nrow = nsim)
G <- 500
Nmax <- 50

# treat_sizes = c(2, 1, 1, 1) # treatment 0 - p_1 individuals, treatment 1 - p_2 individuals, ...
max.support <- Nmax / 10 - 1
# Ng <- rep(Nmax, G)
Ng <- gen.cluster.sizes(G, max.support)

for (s in 1:nsim)
{
  Ng <- gen.cluster.sizes(G, max.support)
  data_pot <- dgp.po.creg(Ng = Ng, tau.vec = tau_vec, G = G, gamma.vec = gamma_vec, n.treat = n_treat)
  proba <- dgp.obs.creg(baseline = data_pot, n.treat = n_treat, k = k, treat_sizes = treat_sizes)
  data_cl <- data.frame("Y" = proba$Y, "D" = proba$D, proba$X, "S" = proba$S, "Ng" = proba$Ng, "G.id" = proba$G.id)
  Y <- data_cl$Y
  D <- data_cl$D
  X <- data.frame("x_1" = data_cl$x_1, 'x_2' = data_cl$x_2)

  S <- data_cl$S
  G.id <- data_cl$G.id
  Ng <- data_cl$Ng
  data_full <- data.frame(Y, D, X, S, G.id, Ng)
  #X <- data.frame("x_1" = data_full$x_1, 'x_2' = data_full$x_2)

  tau_hat <- theta_hat_mult_cl(Y, D, X, S, G.id, Ng)
  var_hat <- var_hat_mult_cl(Y, D, X, S, G.id, Ng, fit = tau_hat) / G
  
  tau_hat_1 <- tau.hat.creg.ss(Y, D, X, S, G.id, Ng)
  var_hat_1 <- as.var.creg.ss(Y, D, X, S, G.id, Ng, tau_hat_1, HC1 = FALSE) / G
  tau_hat_1 <- tau.hat.creg.ss(Y, D, X = NULL, S, G.id, Ng)
  var_hat_1 <- as.var.creg.ss(Y, D, X = NULL, S, G.id, Ng) / G

  agg_result <- res.creg.ss(Y, S, D, G.id, Ng = NULL, X = X, HC1 = TRUE)
  tau_hat_1  = tau.hat.creg.ss(Y, D, X = X, S, G.id, Ng = NULL)
  as.var.creg.ss(Y, D, X, S, G.id, Ng = NULL, tau_hat_1, HC1 = FALSE) / G
  head(agg_result$lin.adj)
  !check.cluster(data.frame("G.id" = agg_result$data$G.id, agg_result$lin.adj))
  X <- data.frame('Ng' = data_cl$Ng, 'x_2' = data_cl$x_2)
  result <- sreg(Y, S = S, D, G.id, Ng = NULL, X = NULL, HC1 = TRUE, small.strata = TRUE)
  result
  result$small.strata
  # tau_hat_old           <- theta_hat_mult_cl_old(Y, D, X, S, G.id, Ng)
  # var_hat_old           <- var_hat_mult_cl_old(Y, D, X, S, G.id, Ng, tau.hat = tau_hat_old) / G
  tau_hat_mtrx[s, ] <- tau_hat$tau.hat
  # tau_hat_mtrx_old[s, ] <- tau_hat_old$tau.hat
  var_hat_mtrx[s, ] <- var_hat
  # var_hat_old_mtrx[s, ] <- var_hat_old
  upper <- tau_hat$tau.hat + qnorm(0.975) * sqrt(var_hat)
  lower <- tau_hat$tau.hat - qnorm(0.975) * sqrt(var_hat)
  hit_mtrx[s, ] <- (tau_vec < upper) & (tau_vec > lower)
  # var_hat             <- var_hat_mult_cl(Y = data_cl$Y, D = data_cl$D, X = data_cl$x_1, S = data_cl$S, G.id = data_cl$G.id, Ng = data_cl$Ng, tau.hat = tau_hat) / G
  # var_hat_mtrx[s, ]   <- var_hat
  # upper               <- tau_hat$tau.hat + qnorm(0.975) * sqrt(var_hat)
  # lower               <- tau_hat$tau.hat - qnorm(0.975) * sqrt(var_hat)
  # hit_mtrx[s, ]       <- (tau_vec < upper) & (tau_vec > lower)
  print(s)
}

colMeans(tau_hat_mtrx)
colMeans(tau_hat_mtrx_old)
apply(tau_hat_mtrx, 2, var)
colMeans(var_hat_mtrx)
apply(tau_hat_mtrx_old, 2, var)
colMeans(hit_mtrx)
```

theta_hat_mult <- function(Y, D, X, S)
{
    tau.hat <- numeric(max(D))
    beta.hat <- matrix(ncol = ncol(X), nrow = max(D))
    data_full <- data.frame(Y, D, X, S)
    for (d in 1:max(D))
    {
    # Compute averages for treated and control within each stratum
#agg_data <- data_full %>%
#  group_by(S) %>%
#  summarize(
#    Y_treated = mean(Y[D == d], na.rm = TRUE),
#    Y_control = mean(Y[D == 0], na.rm = TRUE),
#    X_treated = list(colMeans(X[D == d, , drop = FALSE], na.rm = TRUE)),
#    X_control = list(colMeans(X[D == 0, , drop = FALSE], na.rm = TRUE)),
#    k = n(),
#    l = sum(D == d),
#    q = sum(D == 0), 
#    .groups = "drop"
#  ) 

  agg_data <- data_full %>%
  group_split(S) %>%
  map_dfr(~{
    df <- .
    list(
      S = df$S[1],
      Y_treated = mean(df$Y[df$D == d], na.rm = TRUE),
      Y_control = mean(df$Y[df$D == 0], na.rm = TRUE),
      X_treated = list(colMeans(df[df$D == d, grep("^x_", names(df)), drop = FALSE])), # mean value among treated in each stratum
      X_control = list(colMeans(df[df$D == 0, grep("^x_", names(df)), drop = FALSE])), # mean value among control in each stratum
      k = nrow(df),
      l = sum(df$D == d),
      q = sum(df$D == 0)
    )
  })

# Create Y_diff vector
  Y_diff <- with(agg_data, Y_treated - Y_control)
# Compute differences correctly: row-wise for each pair of treated/control vectors
X_diff_mat <- map2(agg_data$X_treated, agg_data$X_control,
                   ~ .x - .y) %>%
  do.call(rbind, .)
#print(X_diff_mat)
#print(Y_diff)
  


data_decomp <- as.data.frame(agg_data)  
X_treated_mat <- do.call(rbind, data_decomp$X_treated)
X_control_mat <- do.call(rbind, data_decomp$X_control)


lm_model <- lm(Y_diff ~ ., data = as.data.frame(cbind(Y_diff, X_diff_mat)))

#print(summary(lm_model))
beta_hat <- unname(lm_model$coefficients[-1])

X_mat <- as.matrix(data_full[, grepl("^x_", names(data_full))])
print(X_mat)
X_bar <- colMeans(X_mat)
X_dem <- sweep(X_mat, 2, X_bar)

# adjusted estimator:
theta_hat_adj <- sum((data_full$Y * (data_full$D == d))) / sum((data_full$D == d)) -
                 sum((data_full$Y) * (data_full$D == 0)) / sum(data_full$D == 0) -
                 as.numeric(t(colMeans(X_dem[data_full$D == d, , drop = FALSE]) -
                             colMeans(X_dem[data_full$D == 0, , drop = FALSE])) %*% beta_hat)
tau.hat[d] <- theta_hat_adj
beta.hat[d, ] <- beta_hat
    }

ret_list <- list(
    tau.hat = tau.hat,
    beta.hat = beta.hat
)
return(ret_list)
}



theta_hat_mult_cl_old <- function(Y, D, X, S, G.id, Ng)

{   
    tau.hat <- numeric(max(D))
    beta.hat <- numeric(max(D))
    
    working.df <- data.frame(Y, S, D, G.id, Ng, X)
    Y.bar.g <- aggregate(Y ~ G.id, working.df, mean)
    #print(Y.bar.g)
    cl.lvl.data <- unique(working.df[, c("G.id", "D", "S", "Ng", names(working.df)[6:ncol(working.df)])])
    cl.lvl.data <- data.frame("Y.bar" = Y.bar.g$Y, cl.lvl.data)
    data <- cl.lvl.data
    N.bar.G <- mean(data$Ng) #??? Why is this so weird?
    #N.bar.G <- Ng
    #print(N.bar.g)

    #print(data)
    #print(head(working.df, 200))
    #print(data)
    for (d in 1:max(D))
    {
    # Compute averages for treated and control within each stratum
    agg_data <- data %>%
        group_by(S) %>%
    summarise(
        Y_treated = mean(Y.bar[D == d] * N.bar.G, na.rm = TRUE),
        Y_control = mean(Y.bar[D == 0] * N.bar.G, na.rm = TRUE),
        X_treated = mean(x_1[D == d], na.rm = TRUE),
        X_control = mean(x_1[D == 0], na.rm = TRUE),
        k = n(),           # Total units in stratum (should be 2)
        l = sum(D == d),   # Number of treated units (should be 1)
        q = sum(D == 0)
    ) %>%
  mutate(
        Y_diff = (1/l) * Y_treated - (1/q) * Y_control,
        X_diff = (1/l) * X_treated - (1/q) * X_control,
        k = k,
        l = l, 
        q = q
  )


data_decomp <- as.data.frame(agg_data)  
#print(data_decomp)
# run the linear model for covariate adjustments
lm_model <- lm(Y_diff ~ X_diff, data = data_decomp)
print(summary(lm_model))
beta_hat <- coef(lm_model)[2]
X_bar <- mean(data$x_1)
X_dem <- data$x_1 - X_bar
# adjusted estimator:
theta_hat_adj <- sum((data$Y.bar * data$Ng * (data$D == d))) / sum((data$D == d) * data$Ng) -
                    sum(data$Y.bar * data$Ng * (data$D == 0)) / sum((data$D == 0) * data$Ng) -
                    (sum(X_dem * (data$D == d)) / sum((data$D == d) * data$Ng) - 
                    sum(X_dem * (data$D == 0)) / sum((data$D == 0) * data$Ng)) * beta_hat
tau.hat[d] <- theta_hat_adj
beta.hat[d] <- beta_hat
    }
#return(c(tau.hat, beta.hat)) #NB! WORK ON THE WAY HOW TO EXTRACT BOTH SEPARATELY! -- DONE!
#return(tau.hat)
ret_list <- list(
    tau.hat = tau.hat,
    beta.hat = beta.hat
)
return(ret_list)
}

################## try to parallelize ####################
library(devtools) # install devtools
library(sreg)
library(sandwich)
library(lubridate)
library(compiler)
library(extraDistr)
library(VGAM)
library(Matrix)
library(parallel)
library(progress)
library(purrr)
library(SimDesign)
library(pbapply)

###############
rm(list = ls())
###############
options(scipen = 999) # disable scientific notation



num_cores <- detectCores()
cl <- makeCluster(num_cores, outfile = "")

# Upload the libraries to the cluster
clusterEvalQ(cl, {
  library(lubridate)
  library(compiler)
  library(extraDistr)
  library(Matrix)
  library(progress)
  library(parallel)
  library(sreg)
  library(pbapply)
  library(dplyr)
  library(purrr)
  library(tidyverse)
  source("/Users/trifonovjuri/Desktop/sreg/R/2.0(dev)/fun_new.r")
})

sim.func <- function(sim.id) {
  seed <- 1000 + sim.id
  set.seed(seed)

  # --- DGP settings ---
  n.treat <- 2
  tau.vec <- c(0.2, 1.2)   # true ATEs
  gamma.vec <- c(0.4, 0.2, 1)
  k <- 4
  treat_sizes <- c(1, 1, 2)
  G <- 12000
  Nmax <- 50
  max.support <- Nmax / 10 - 1

  # --- Generate data ---
  Ng <- gen.cluster.sizes(G, max.support)
  data_pot <- dgp.po.creg(Ng = Ng, tau.vec = tau.vec, G = G, gamma.vec = gamma.vec, n.treat = n.treat)
  proba <- dgp.obs.creg(baseline = data_pot, n.treat = n.treat, k = k, treat_sizes = treat_sizes)

  data_cl <- data.frame(
    Y = proba$Y,
    D = proba$D,
    proba$X,
    S = proba$S,
    Ng = proba$Ng,
    G.id = proba$G.id
  )

  Y <- data_cl$Y
  D <- data_cl$D
  X <- data.frame("x_1" = data_cl$x_1)  # or include other covariates as needed
  S <- data_cl$S
  G.id <- data_cl$G.id
  Ng <- data_cl$Ng

  result <- tryCatch({
    # Estimate ATEs and variances
    theta_res <- theta_hat_mult_cl(Y, D, X, S, G.id, Ng)
    tau_hat <- theta_res$tau.hat
    var_hat <- var_hat_mult_cl(Y, D, X, S, G.id, Ng, fit = theta_res) / G
    se_hat <- sqrt(var_hat)

    # Confidence intervals and coverage
    CI.left <- tau_hat - qnorm(0.975) * se_hat
    CI.right <- tau_hat + qnorm(0.975) * se_hat
    tstat <- tau_hat / se_hat
    ci.hit <- as.numeric(tau.vec >= CI.left & tau.vec <= CI.right)

    list(
      tau = tau_hat,
      se = se_hat,
      tstat = tstat,
      CI.left = CI.left,
      CI.right = CI.right,
      ci.hit = ci.hit
    )
  },
  error = function(e) {
    cat("Simulation", sim.id, "encountered an error:", conditionMessage(e), "\n")
    list(
      tau = NA,
      se = NA,
      tstat = NA,
      CI.left = NA,
      CI.right = NA,
      ci.hit = NA
    )
  })

  return(result)
}

simres <- pblapply(1:50000, sim.func, cl=cl)
stopCluster(cl)
tau <- na.omit(as.matrix(sapply(simres, function(simres) simres$tau)))
se <- na.omit(as.matrix(sapply(simres, function(simres) simres$se)))
ci.hit <- na.omit(as.matrix(sapply(simres, function(simres) simres$ci.hit)))
rowMeans(tau)
apply(tau, 1, sd)
rowMeans(se)
rowMeans(ci.hit)








library("sreg")
library("dplyr")
library("haven")
#' ### Example 1. Simulated Data.
data <- sreg.rgen(n = 1200, tau.vec = c(0.2, 0.5, 0.8), n.strata = 4, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
Y <- data$Y
head(data)

S <- data$S
D <- data$D
X <- data.frame("age" = data$x_1, "sex" = data$x_2)
G.id <- data$G.id
Ng <- data$Ng
result <- sreg(Y, S, D, G.id = G.id, Ng = Ng, X)
sreg(Y, S = S, D, G.id = NULL, Ng = NULL, X = X)
print(result)
plot(result)



dtapm <- sreg.rgen(n = 100, tau.vec = c(1.2), cluster = TRUE, small.strata = TRUE, k = 2, treat.sizes = c(1, 1))
result <- sreg(Y = dtapm$Y, S = dtapm$S, D = dtapm$D, X = dtapm$X, small.strata = TRUE, G.id = dtapm$G.id, Ng = dtapm$Ng)
result
head(dtapm)
data <- sreg.rgen(n = 300, tau.vec = c(1.2, 0.8), cluster = FALSE, small.strata = TRUE, k = 3, treat.sizes = c(1, 1, 1))
head(data)

result <- sreg(Y = data$Y, S = data$S, D = data$D, X = data.frame('x_1' = data$x_1, 'x_2' = data$x_2), small.strata = TRUE)
print(result)

max(result$data$S)

length(result$data$Y) / max(result$data$S)


data("AEJapp")
data <- AEJapp
Y <- data$gradesq34
D <- data$treatment
S <- data$class_level
data.clean <- data.frame(Y, D, S)
data.clean <- data.clean %>%
  mutate(D = ifelse(D == 3, 0, D))
Y <- data.clean$Y
D <- data.clean$D
S <- data.clean$S
head(data.clean)

result <- sreg::sreg(Y = Y, S = S, D = D)
print(result)

pills <- data$pills_taken
age <- data$age_months
data.clean <- data.frame(Y, D, S, pills, age)
data.clean <- data.clean %>%
  mutate(D = ifelse(D == 3, 0, D))
Y <- data.clean$Y
D <- data.clean$D
S <- data.clean$S
X <- data.frame("pills" = data.clean$pills, "age" = data.clean$age)
result <- sreg::sreg(Y, S, D, G.id = NULL, X = X)
print(result)


result





plot_sreg_results <- function(result) {
  # Load ggplot2
  library(ggplot2)

  # Construct a data frame from result
  df <- data.frame(
    treatment = factor(seq_along(result$tau.hat)),  # factor for x-axis
    tau = result$tau.hat,
    CI.lower = result$CI.left,
    CI.upper = result$CI.right
  )

  # Create the plot
  ggplot(df, aes(x = treatment, y = tau)) +
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = CI.lower, ymax = CI.upper), width = 0.1) +
    labs(
      x = "Treatment Group",
      y = "Estimated ATE",
      title = "Point Estimates and Confidence Intervals for ATE"
    ) +
    theme_minimal()
}

plot_sreg_results_fancy <- function(result) {
  library(ggplot2)

  df <- data.frame(
    treatment = factor(seq_along(result$tau.hat)),
    tau = result$tau.hat,
    CI.lower = result$CI.left,
    CI.upper = result$CI.right
  )

  # Add numeric version of treatment for proper ribbon plotting
  df$treatment_num <- as.numeric(df$treatment)

  ggplot(df, aes(x = treatment_num, y = tau)) +
    # Confidence interval ribbon with transparency
    geom_ribbon(aes(ymin = CI.lower, ymax = CI.upper), fill = "#1f78b4", alpha = 0.2) +
    # ATE point estimates
    geom_point(size = 4, color = "#1f78b4") +
    # Optional dashed line connecting points
    geom_line(color = "#1f78b4", linetype = "dashed") +
    # Horizontal line at 0
    geom_hline(yintercept = 0, linetype = "dotted", color = "gray40") +
    # Set treatment labels on x-axis
    scale_x_continuous(
      breaks = df$treatment_num,
      labels = df$treatment
    ) +
    labs(
      x = "Treatment Group",
      y = "Estimated ATE",
      title = "Estimated ATEs with Confidence Intervals"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      axis.title = element_text(face = "bold"),
      panel.grid.major.y = element_line(color = "gray90")
    )
}
plot_sreg_results(result)
plot_sreg_results_fancy(result)
plot_sreg_horizontal(result)
plot_sreg_horizontal <- function(result, treatment_labels = NULL) {
  library(ggplot2)

  df <- data.frame(
    treatment = seq_along(result$tau.hat),
    tau = result$tau.hat,
    CI.lower = result$CI.left,
    CI.upper = result$CI.right,
    SE = round((result$CI.right - result$tau.hat) / 1.96, 2)
  )

  if (!is.null(treatment_labels)) {
    df$label <- factor(treatment_labels, levels = rev(treatment_labels))
  } else {
    df$label <- factor(paste("Treatment", df$treatment), levels = rev(paste("Treatment", df$treatment)))
  }

  ggplot(df, aes(y = label)) +
    # Horizontal CI bar
    geom_rect(aes(xmin = CI.lower, xmax = CI.upper, ymin = as.numeric(label) - 0.01, ymax = as.numeric(label) + 0.01),
              fill = "#2c3e50", alpha = 0.8) +
    # Diamond-shaped point
    geom_point(aes(x = tau), shape = 23, size = 3, fill = "white", stroke = 1.2, color = "black") +
    # Text label with tau (SE)
    geom_text(aes(x = tau, label = sprintf("%.2f (%.2f)", tau, SE)),
              vjust = -1.5, color = "black", size = 4) +
    # Vertical line at 0
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
    labs(
      x = "Treatment Effect",
      y = NULL,
      title = "Estimated ATEs with Confidence Intervals"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.y = element_text(hjust = 1),
      axis.title.x = element_text(face = "bold")
    )
}

result

plot_sreg_horizontal <- function(result, treatment_labels = NULL) {
  library(ggplot2)

  df <- data.frame(
    treatment = seq_along(result$tau.hat),
    tau = result$tau.hat,
    CI.lower = result$CI.left,
    CI.upper = result$CI.right,
    SE = result$se.rob
  )

  if (!is.null(treatment_labels)) {
    df$label <- factor(treatment_labels, levels = rev(treatment_labels))
  } else {
    df$label <- factor(paste("Treatment", df$treatment), levels = rev(paste("Treatment", df$treatment)))
  }

  ggplot(df, aes(y = label)) +
    geom_rect(aes(
      xmin = CI.lower,
      xmax = CI.upper,
      ymin = as.numeric(label) - 0.01,
      ymax = as.numeric(label) + 0.01,
      fill = tau
    ), alpha = 0.8) +
    geom_point(aes(x = tau), shape = 23, size = 3, fill = "white", stroke = 1.2, color = "black") +
    geom_text(aes(x = tau, label = sprintf("%.2f (%.2f)", tau, SE)),
              vjust = -1.5, color = "black", size = 4) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
    scale_fill_viridis_c(option = "viridis", name = "Effect Size") +
    #scale_fill_gradient(low = "#bdd7e7", high = "#08519c", name = "Effect Size") +
    labs(
      x = "Treatment Effect",
      y = NULL,
      title = "Estimated ATEs with Confidence Intervals"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      axis.text.y = element_text(hjust = 1),
      axis.title.x = element_text(face = "bold"),
      legend.position = "right"
    )
}


library(viridis)
plot_sreg_horizontal(result)



result
plot(result)

class(result)



<!-- design.classifier <- function(data, S) {
  S_sym <- rlang::ensym(S)

  # Step 1: Compute stratum sizes
  strata_sizes <- data %>%
    group_by(!!S_sym) %>%
    summarise(size = n(), .groups = "drop")

  unique_sizes <- unique(strata_sizes$size)

  if (length(unique_sizes) == 1) {
    # All strata are the same size — no mixed design
    return(data)
  }

  # Step 2: Find modal stratum size (the "small strata" size)
  modal_size <- strata_sizes %>%
    count(size) %>%
    arrange(desc(n)) %>%
    slice(1) %>%
    pull(size)

  # Step 3: Classify each stratum
  strata_sizes <- strata_sizes %>%
    mutate(stratum_type = ifelse(size == modal_size, "small", "big"))

  # Step 4: Join classification back to full dataset
  data_classified <- data %>%
    left_join(strata_sizes, by = rlang::as_string(S_sym))

  # Step 5: Issue warning
  warning("Mixed design detected: strata of varying sizes found. Weighted estimators will be used.")

  return(data_classified)
} -->
```{r}
# ------------------------------------------------------------------
#  Classify strata as "small" or "big" in a mixed design
# ------------------------------------------------------------------
# design.classifier <- function(data, S, G.id = NULL, keep.size = FALSE, warn = TRUE) {
#   ## 1. Capture column names (works with bare names or strings)
#   S_name <- if (is.character(substitute(S))) substitute(S) else deparse(substitute(S))
#   G_name <- if (!missing(G.id)) {
#     if (is.character(substitute(G.id))) substitute(G.id) else deparse(substitute(G.id))
#   } else {
#     NULL
#   }

#   ## 2. Compute stratum sizes
#   if (!is.null(G_name)) {
#     # -- clustered: count *clusters* per stratum
#     cluster_strata <- dplyr::distinct(data, .data[[S_name]], .data[[G_name]])
#     strata_sizes   <- dplyr::count(cluster_strata, .data[[S_name]], name = "size")
#   } else {
#     # -- individual: count *units* per stratum
#     strata_sizes   <- dplyr::count(data, .data[[S_name]], name = "size")
#   }

#   ## 3. If every stratum has the same size, nothing to classify
#   if (length(unique(strata_sizes$size)) == 1) {
#     if (!keep.size) strata_sizes$size <- NULL  # cosmetic
#     return(dplyr::left_join(data, strata_sizes, by = S_name))
#   }

#   ## 4. Find the modal size and classify
#   modal_size <- strata_sizes %>%
#     dplyr::count(size) %>%
#     dplyr::arrange(dplyr::desc(n)) %>%
#     dplyr::pull(size) %>%
#     .[[1]]

#   strata_sizes <- strata_sizes %>%
#     dplyr::mutate(stratum_type = ifelse(size == modal_size, "small", "big"))

#   if (!keep.size) strata_sizes$size <- NULL

#   ## 5. Merge back and optionally warn
#   out <- dplyr::left_join(data, strata_sizes, by = S_name)

#   if (warn)
#     warning("Mixed design detected: strata of varying cluster/unit counts. ",
#             "Weighted estimators will be used.", call. = FALSE)

#   return(out)
# }
```

data_s <- sreg.rgen(n = 3000, tau.vec = c(0.2, 0.8), n.strata = 4, cluster = TRUE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S
#sreg(Y = data_s$Y, S = data_s$S, D = data_s$D, G.id = data_s$G.id, Ng = data_s$Ng, X = NULL, small.strata = TRUE)
#pum <- res.creg.ss(Y = data_s$Y, D = data_s$D, S = data_s$S, G.id = data_s$G.id, Ng = data_s$Ng, X = data.frame(data_s$x_1, data_s$x_2), HC1 = FALSE)
S <- data_s$S
#pum$tau.hat
#pum$se.rob
data_b <- sreg.rgen(n = 50, tau.vec = c(0.2, 0.8), n.strata = 2, cluster = TRUE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

# 🧠 Step 4: Make cluster IDs unique across the two datasets!!!!!
max_gid <- max(data_s$G.id)
data_b$G.id <- data_b$G.id + max_gid
length(intersect(data_s$G.id, data_b$G.id)) == 0

data <- rbind(data_s[, -ncol(data_s)], data_b)
S <- data$S
G.id <- data$G.id

design.classifier(data, S, G.id)

## ----- ## ----- ## ----- ## ---- ## ----- #

# Step 1: Classify strata
data_all <- design.classifier(data, S, G.id)

# Step 2: Split the data
data_small <- dplyr::filter(data_all, stratum_type == "small")
data_big   <- dplyr::filter(data_all, stratum_type == "big")

#sreg(Y = data_small$Y, S = data_small$S, D = data_small$D, G.id = data_small$G.id, Ng = data_small$Ng, X = NULL, small.strata = TRUE)

# Step 3: Run the estimators
#res_small <- res.sreg.ss(Y = data_small$Y, D = data_small$D, S = data_small$S, X = data_small[, grep("^x_", names(data_small)), drop = FALSE], HC1 = TRUE)
res_small <- res.sreg.ss(Y = data_small$Y, D = data_small$D, S = data_small$S, X = data.frame(data_small$x_1, data_small$x_2), HC1 = TRUE)
res_small <- res.creg.ss(Y = data_small$Y, D = data_small$D, S = data_small$S, G.id = data_small$G.id, Ng = data_small$Ng, X = data.frame(data_small$x_1, data_small$x_2), HC1 = FALSE)
res_small$tau.hat
res_small$se.rob


#res_big <- res.sreg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = data_big[, grep("^x_", names(data_big)), drop = FALSE], HC1 = TRUE)
res_big <- res.sreg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = NULL, HC1 = TRUE)
res_big <- res.creg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = NULL, G.id = data_big$G.id, Ng = data_big$Ng, HC1 = FALSE)
res_big$tau.hat
res_big$se.rob

# Step 4: Combine estimates
N_small <- nrow(data_small)
N_big   <- nrow(data_big)
N_total <- N_small + N_big

tau_hat <- (N_small / N_total) * res_small$tau.hat + (N_big / N_total) * res_big$tau.hat

se_combined <- sqrt((N_small / N_total)^2 * res_small$se.rob^2 +
                    (N_big   / N_total)^2 * res_big$se.rob^2)

```


## Simulations for the combined estimator (sreg)
```{r}
nsim = 1000
tau.vec = c(0.2, 0.8)
n.treat = length(tau.vec)
n_1 = 3000
n_2 = 50

theta_hat_mtrx <- matrix(ncol = n.treat, nrow = nsim)

se_hat_mtrx <- matrix(ncol = n.treat, nrow = nsim)
hit <- matrix(ncol = n.treat, nrow = nsim)

for (s in 1:nsim)
{
data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]


data <- rbind(data_s, data_b)

## ----- ## ----- ## ----- ## ---- ## ----- #

# Step 1: Classify strata
data_all <- design.classifier(data, S)

# Step 2: Split the data
data_small <- dplyr::filter(data_all, stratum_type == "small")
data_big   <- dplyr::filter(data_all, stratum_type == "big")

# Step 3: Run the estimators
#res_small <- res.sreg.ss(Y = data_small$Y, D = data_small$D, S = data_small$S, X = data_small[, grep("^x_", names(data_small)), drop = FALSE], HC1 = TRUE)
res_small <- res.sreg.ss(Y = data_small$Y, D = data_small$D, S = data_small$S, X = NULL, HC1 = FALSE)

#res_big <- res.sreg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = data_big[, grep("^x_", names(data_big)), drop = FALSE], HC1 = TRUE)
res_big <- res.sreg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = NULL, HC1 = FALSE)


# Step 4: Combine estimates
N_small <- nrow(data_small)
N_big   <- nrow(data_big)
N_total <- N_small + N_big

tau_hat <- (N_small / N_total) * res_small$tau.hat + (N_big / N_total) * res_big$tau.hat

se_combined <- sqrt((N_small / N_total)^2 * res_small$se.rob^2 +
                    (N_big   / N_total)^2 * res_big$se.rob^2)

theta_hat_mtrx[s, ] <- tau_hat
se_hat_mtrx[s, ] <- se_combined

upper <- tau_hat + qnorm(0.975) * se_combined
lower <- tau_hat - qnorm(0.975) * se_combined
hit[s, ] <- (tau.vec < upper) & (tau.vec > lower)
print(s)
}

result_table <- data.frame(
  `True tau` = tau.vec,
  `E[tau_n]` = round(colMeans(theta_hat_mtrx), 4),
  `True Variance` = round(colMeans(se_hat_mtrx), 4),
  `E[V_n]` = round(apply(theta_hat_mtrx, 2, sd), 4),
  `Coverage` = round(colMeans(hit), 4),
  check.names = FALSE
)
print(result_table)
```
## Simulations for the combined estimator (creg)
```{r}
nsim = 1000
tau.vec = c(0.2, 0.8)
n.treat = length(tau.vec)
n_1 = 3000
n_2 = 50

theta_hat_mtrx <- matrix(ncol = n.treat, nrow = nsim)

se_hat_mtrx <- matrix(ncol = n.treat, nrow = nsim)
hit <- matrix(ncol = n.treat, nrow = nsim)

for (s in 1:nsim)
{
data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = TRUE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = TRUE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

# 🧠 Step 4: Make cluster IDs unique across the two datasets!!!!!
max_gid <- max(data_s$G.id)
data_b$G.id <- data_b$G.id + max_gid
length(intersect(data_s$G.id, data_b$G.id)) == 0

data <- rbind(data_s[, -ncol(data_s)], data_b)

## ----- ## ----- ## ----- ## ---- ## ----- #

# Step 1: Classify strata
data_all <- design.classifier(data, S, G.id)

# Step 2: Split the data
data_small <- dplyr::filter(data_all, stratum_type == "small")
data_big   <- dplyr::filter(data_all, stratum_type == "big")

# Step 3: Run the estimators
#res_small <- res.sreg.ss(Y = data_small$Y, D = data_small$D, S = data_small$S, X = data_small[, grep("^x_", names(data_small)), drop = FALSE], HC1 = TRUE)
res_small <- res.creg.ss(Y = data_small$Y, D = data_small$D, S = data_small$S, X = data.frame(data_small$x_1, data_small$x_2), G.id = data_small$G.id, Ng = data_small$Ng, HC1 = TRUE)

#res_big <- res.sreg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = data_big[, grep("^x_", names(data_big)), drop = FALSE], HC1 = TRUE)
res_big <- res.creg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = NULL, G.id = data_big$G.id, Ng = data_big$Ng, HC1 = FALSE)
#res_big <- res.creg(Y = data_big$Y, D = data_big$D, S = data_big$S, X = data.frame(data_big$x_1, data_big$x_2), G.id = data_big$G.id, Ng = data_big$Ng, HC1 = TRUE)
res_big$tau.hat
res_big$se.rob

# Step 4: Combine estimates
N_small <- nrow(data_small)
N_big   <- nrow(data_big)
N_total <- N_small + N_big

tau_hat <- (N_small / N_total) * res_small$tau.hat + (N_big / N_total) * res_big$tau.hat

se_combined <- sqrt((N_small / N_total)^2 * res_small$se.rob^2 +
                    (N_big   / N_total)^2 * res_big$se.rob^2)

theta_hat_mtrx[s, ] <- tau_hat
se_hat_mtrx[s, ] <- se_combined

upper <- tau_hat + qnorm(0.975) * se_combined
lower <- tau_hat - qnorm(0.975) * se_combined
hit[s, ] <- (tau.vec < upper) & (tau.vec > lower)
print(s)
}

result_table <- data.frame(
  `True tau` = tau.vec,
  `E[tau_n]` = round(colMeans(theta_hat_mtrx), 4),
  `True Variance` = round(colMeans(se_hat_mtrx), 4),
  `E[V_n]` = round(apply(theta_hat_mtrx, 2, sd), 4),
  `Coverage` = round(colMeans(hit), 4),
  check.names = FALSE
)
print(result_table)
```

```{r}
data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = TRUE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = TRUE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

# 🧠 Step 4: Make cluster IDs unique across the two datasets!!!!!
max_gid <- max(data_s$G.id)
data_b$G.id <- data_b$G.id + max_gid
length(intersect(data_s$G.id, data_b$G.id)) == 0

data <- rbind(data_s[, -ncol(data_s)], data_b)
resultim <- res.sreg.mixed(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), HC1 = TRUE)
resultim$tau.hat
resultim$se.rob

##### no clusters #####
data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

# 🧠 Step 4: Make cluster IDs unique across the two datasets!!!!!
max_gid <- max(data_s$G.id)
data_b$G.id <- data_b$G.id + max_gid
length(intersect(data_s$G.id, data_b$G.id)) == 0

data <- rbind(data_s, data_b)
resultim <- res.sreg.mixed(Y = data$Y, S = data$S, D = data$D,  X = NULL, HC1 = TRUE)
resultim$tau.hat
resultim$se.rob



```

# Testing the native sreg with the mixed design function
```{r}
##### no clusters #####
data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

data <- rbind(data_s, data_b)
resultim <- res.sreg.mixed(Y = data$Y, S = data$S, D = data$D,  X = NULL, HC1 = TRUE)
resultim$tau.hat
resultim$se.rob


res_sreg <- sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), HC1 = FALSE, small.strata = TRUE)
print(res_sreg)
res_sreg$tau.hat
res_sreg$se.rob





data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = TRUE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = TRUE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

# 🧠 Step 4: Make cluster IDs unique across the two datasets!!!!!
max_gid <- max(data_s$G.id)
data_b$G.id <- data_b$G.id + max_gid
length(intersect(data_s$G.id, data_b$G.id)) == 0

data <- rbind(data_s[, -ncol(data_s)], data_b)
resultim <- res.creg.mixed(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE)
resultim$tau.hat
resultim$se.rob

result_creg <- sreg(Y = data$Y, S = data$S, D = data$D, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = TRUE)
promo <- res.creg.mixed(Y = data$Y, S = data$S, D = data$D, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE)
promo$tau.hat
promo$se.rob
length(promo$lin.adj[,1])
length(promo$data$G.id)
print(result_creg)
```

# Let's run some tests to ensure that everything is working (no clusters)
```{r}
# Test 1. data: small strata, option: small strata
set.seed(123)
tau.vec = c(0.2, 0.8)
n.treat = length(tau.vec)
n_1 = 300

data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = FALSE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = NULL, X = data.frame(data$x_1), HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = NULL, D = NULL, S = data$S, X = data.frame(data$x_1), HC1 = TRUE, small.strata = TRUE)
print(result)


# Test 2. data: big strata, option: big strata
tau.vec = c(0.2, 0.9, 1.5)
n.treat = length(tau.vec)
n_1 = 1000

data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1, 1), k = 3)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = TRUE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = TRUE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = TRUE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = FALSE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), HC1 = TRUE, small.strata = FALSE)
print(result)


# Test 3. data: small strata, option: big strata
set.seed(123)
tau.vec = c(0.2, 0.8)
n.treat = length(tau.vec)
n_1 = 900

data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = TRUE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = TRUE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = FALSE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = FALSE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), HC1 = TRUE, small.strata = FALSE)
print(result)

nsim = 1000
tau_small <- matrix(nrow = nsim, ncol = length(tau.vec)) 
tau_big   <- matrix(nrow = nsim, ncol = length(tau.vec))
se_small  <- matrix(nrow = nsim, ncol = length(tau.vec))
se_big    <- matrix(nrow = nsim, ncol = length(tau.vec))
for (s in 1:nsim){
  data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = TRUE, treat.sizes = c(1, 1), k = 2)
  result_big <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = TRUE, small.strata = FALSE)
  result_small <- sreg(Y = data$Y, D = data$D, S = data$S, X = NULL, HC1 = FALSE, small.strata = TRUE)
  tau_small[s, ] <- result_small$tau.hat
  tau_big[s, ]   <- result_big$tau.hat
  se_small[s, ]  <- result_small$se.rob
  se_big[s, ]    <- result_big$se.rob
  print(s)
}
apply(tau_small, 2, sd)
colMeans(se_big)
colMeans(se_small)


# Test 4. data: big strata, option: small strata 
tau.vec = c(0.2, 0.9)
n.treat = length(tau.vec)
n_1 = 1000
data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 20, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
head(data)
sreg(Y = data$Y, D = data$D, S = data$S, small.strata = TRUE)

# Test 5. data: mixed design, option: small strata (so we should have just a mixed estimator)
tau.vec = c(0.2, 0.9) 
n.treat = length(tau.vec)
n_1 = 3000
n_2 = 50
data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = FALSE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

data <- rbind(data_s, data_b)

proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), HC1 = TRUE, small.strata = TRUE)
proba

# Test 6. data: mixed design, option: big strata (just a big strata estimator, but should through a warning that estimators are invalid!)
proba <- sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), HC1 = FALSE, small.strata = FALSE)
proba
proba <- sreg(Y = data$Y, S = data$S, D = data$D,  X = NULL, HC1 = FALSE, small.strata = FALSE)
proba

```

# Let's run some tests to ensure that everything is working (with clusters)
```{r}
# Test 1. data: small strata, option: small strata
tau.vec = c(0.2, 0.8)
n.treat = length(tau.vec)
n_1 = 900

data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = TRUE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
result <- sreg(Y = data$Y, D = data$D, S = data$S, G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = NULL, HC1 = FALSE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), G.id = NULL, Ng = data$G.id, HC1 = FALSE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = NULL, G.id = data$G.id, Ng = data$G.id, HC1 = TRUE, small.strata = TRUE)
print(result)


# Test 2. data: big strata, option: big strata
tau.vec = c(0.2, 0.9, 1.5)
n.treat = length(tau.vec)
n_1 = 1000

data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = TRUE, small.strata = FALSE, treat.sizes = c(1, 1, 1), k = 3)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = TRUE, G.id = data$G.id, Ng = data$Ng, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, HC1 = FALSE, G.id = data$G.id, Ng = data$Ng, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = TRUE, G.id = data$G.id, Ng = data$Ng, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), HC1 = FALSE, G.id = data$G.id, Ng = data$Ng, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = FALSE)
print(result)

result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), G.id = data$G.id, Ng = NULL, HC1 = FALSE, small.strata = FALSE)
print(result)

# Test 3. data: small strata, option: big strata
tau.vec = c(0.2, 0.8)
n.treat = length(tau.vec)
n_1 = 900

data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = TRUE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
result <- sreg(Y = data$Y, D = data$D, S = data$S, G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = TRUE) # should not match fith small.strata = FALSE unless we change the estimator
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = FALSE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = TRUE)
print(result)
result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = FALSE)
print(result)

result <- sreg(Y = data$Y, D = data$D, S = data$S, X = data.frame(data$x_1), G.id = data$G.id, Ng = NULL, HC1 = TRUE, small.strata = FALSE)
print(result)


# Test 4. data: big strata, option: small strata (should not work and throw a warning)
tau.vec = c(0.2, 0.9)
n.treat = length(tau.vec)
n_1 = 1000
data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 20, cluster = TRUE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
head(data)
sreg(Y = data$Y, D = data$D, S = data$S, G.id = data$G.id, Ng = data$Ng, small.strata = TRUE, HC1 = TRUE)
sreg(Y = data$Y, D = data$D, S = data$S, G.id = data$G.id, Ng = data$Ng, small.strata = TRUE, HC1 = FALSE)
sreg(Y = data$Y, D = data$D, S = data$S, G.id = data$G.id, Ng = data$Ng, X = data.frame(data$x_1), small.strata = TRUE, HC1 = TRUE)
sreg(Y = data$Y, D = data$D, S = data$S, G.id = data$G.id, Ng = NULL, X = data.frame(data$x_1), small.strata = TRUE, HC1 = TRUE)

# Test 4. data: big strata, option: small strata 
tau.vec = c(0.2, 0.9)
n.treat = length(tau.vec)
n_1 = 1000
data <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 20, cluster = FALSE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
head(data)
sreg(Y = data$Y, D = data$D, S = data$S, small.strata = TRUE)

# Test 5. data: mixed design, option: small strata (so we should have just a mixed estimator)
tau.vec = c(0.2, 0.9)
n.treat = length(tau.vec)
n_1 = 3000
n_2 = 50
data_s <- sreg.rgen(n = n_1, tau.vec = tau.vec, n.strata = 4, cluster = TRUE, small.strata = TRUE, treat.sizes = c(1, 1, 1), k = 3)
Y <- data$Y
S <- data$S

data_b <- sreg.rgen(n = n_2, tau.vec = tau.vec, n.strata = 2, cluster = TRUE, small.strata = FALSE, treat.sizes = c(1, 1), k = 2)
# Step 1: Get the max stratum ID in data_s
max_id <- max(data_s$S)

# Step 2: Get unique strata in data_b and assign new IDs
unique_b_strata <- sort(unique(data_b$S))
num_b_strata <- length(unique_b_strata)

# Create a named mapping from old to new stratum IDs
new_ids <- seq(max_id + 1, max_id + num_b_strata)
stratum_map <- setNames(new_ids, unique_b_strata)

# Step 3: Relabel data_b$S
data_b$S <- stratum_map[as.character(data_b$S)]

# 🧠 Step 4: Make cluster IDs unique across the two datasets!!!!!
max_gid <- max(data_s$G.id)
data_b$G.id <- data_b$G.id + max_gid
length(intersect(data_s$G.id, data_b$G.id)) == 0

data <- rbind(data_s[, -ncol(data_s)], data_b)
Y <- data$Y
S <- data$S
G.id <- data$G.id
Ng <- data$Ng
D <- data$D
data_tst <- data.frame(Y = Y, D = D, S = S, G.id = G.id, Ng = Ng)
proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2, data$Ng), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = TRUE)
proba
proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = TRUE)
proba
proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = NULL, G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = TRUE)
proba
proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = NULL, G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = TRUE)
proba
proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = NULL, HC1 = TRUE, small.strata = TRUE)
proba
proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = NULL, HC1 = FALSE, small.strata = TRUE)
proba
proba <-sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), G.id = NULL, Ng = NULL, HC1 = FALSE, small.strata = TRUE)
proba

# Test 6. data: mixed design, option: big strata (just a big strata estimator!)
proba <- sreg(Y = data$Y, S = data$S, D = data$D,  X = data.frame(data$x_1, data$x_2), G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = FALSE)
proba
proba <- sreg(Y = data$Y, S = data$S, D = data$D,  X = NULL, G.id = data$G.id, Ng = data$Ng, HC1 = TRUE, small.strata = FALSE)
proba
proba <- sreg(Y = data$Y, S = data$S, D = data$D,  X = NULL, G.id = data$G.id, Ng = data$Ng, HC1 = FALSE, small.strata = FALSE)
proba
proba <- sreg(Y = data$Y, S = data$S, D = data$D,  X = NULL, G.id = data$G.id, Ng = NULL, HC1 = FALSE, small.strata = FALSE)
proba
```




